Using spatially biased variables in ecosystem condition accounting with a GIS based workflow

### 2024-01-19 manuscript/HIAs.qmd
number of polygons

```{r prepData}
#| eval: false

@@

@@

muni_tbl <- muni3 |>
  # calculate total area
  mutate(area_km = 
           round(
             units::drop_units(
               geom |> st_area() * 1e-6))) |>
  # make tibble for the coming join
  as_tibble() |>
  # paste inn terrestrial area
  left_join(terrestrial |> select(kommunenummer, t_area_km),
            keep=F) |>
  # area of survey
  left_join(dk2 |> select(Municipality, dk_area_km)) |>
  mutate(dk_percent = round((dk_area_km/t_area_km) * 100))

@@

| Municipality | Total terrestrial area (km2)                                                 | \% of terrestrial area surveyed                                            | \% open mires in relation to total terrestrial area | Total mire area | Fraction mire area included in survey | Number of mire polygons in survey |
|-----------|-----------|-----------|-----------|-----------|-----------|-----------|
| Nordre Follo | `r terrestrial |> filter(Municipality == "Nordre Follo") |> pull(t_area_km)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(dk_percent)` |                                                     |                 |                                       |                                   |
| Trondheim    | `r terrestrial |> filter(Municipality == "Trondheim") |> pull(t_area_km)`    | `r muni_tbl |> filter(Municipality == "Trondheim") |> pull(dk_percent)`    |                                                     |                 |                                       |                                   |
| Målselv      | `r terrestrial |> filter(Municipality == "Målselv") |> pull(t_area_km)`      | `r muni_tbl |> filter(Municipality == "Målselv") |> pull(dk_percent)`      |                                                     |                 |                                       |                                   |

>>>>

```{r natureTypeData}
#| eval: false

@@

table(nature3$municipality)

@@

# number and area of mire polygons
nature3_tbl <- nature3 |>
  group_by(Municipality) |>
  summarise(n = n()) |>
  as_tibble()

muni_tbl <- muni3 |>
  # calculate total area
  mutate(area_km = 
           round(
             units::drop_units(
               geom |> st_area() * 1e-6))) |>
  # make tibble for the coming join
  as_tibble() |>
  # paste inn terrestrial area
  left_join(terrestrial |> select(kommunenummer, t_area_km),
            keep=F) |>
  # area of survey
  left_join(dk2 |> select(Municipality, dk_area_km)) |>
  mutate(dk_percent = round((dk_area_km/t_area_km) * 100)) |>
  # number of polygons
  left_join(nature3_tbl |> select(Municipality, n))

@@

| Municipality | Total terrestrial area (km2)                                                 | \% of terrestrial area surveyed                                             | \% open mires in relation to total terrestrial area | Total mire area | Fraction mire area included in survey | Number of mire polygons in survey                                 |
|-----------|-----------|-----------|-----------|-----------|-----------|-----------|
| Nordre Follo | `r terrestrial |> filter(Municipality == "Nordre Follo") |> pull(t_area_km)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(dk_percent)`  |                                                     |                 |                                       | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(n)` |
| Trondheim    | `r terrestrial |> filter(Municipality == "Trondheim") |> pull(t_area_km)`    | `r muni_tbl |> filter(Municipality == "Trondheim") |> pull(dk_percent)`     |                                                     |                 |                                       | `r muni_tbl |> filter(Municipality == "Trondheim") |> pull(n)`    |
| Målselv      | `r terrestrial |> filter(Municipality == "Målselv") |> pull(t_area_km)`      | `r muni_tbl |> filter(Municipality == "Målselv") |> pull(dk_percent)`       |                                                     |                 |                                       | `r muni_tbl |> filter(Municipality == "Målselv") |> pull(n)`      |
